Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-04-30 analysis/paper/asymsam.Rmd
Termina la tabla de cor ENSO-SAM

```{r enso-cor-table}
table <- enso_cors %>% 
  .[index == "oni"] %>% 
  .[, p.value := p.adjust(p.value, "fdr")] %>% 
  .[, p.value := scales::pvalue(p.value)] %>% 
  .[, cor_text := paste0(round(cor, 2), "\n(", p.value, ")")] %>% 
  .[, term := lab_sam[term]] %>% 
  dcast(season ~ term, value.var = "cor_text") %>% 
  setcolorder(c("season",lab_sam))

# table2 <- enso_cors %>% 
#   .[index == "oni"] %>% 
#   .[, p.value := p.adjust(p.value, "fdr")] %>% 
#   # .[, p.value := scales::pvalue(p.value)] %>% 
#   # .[, cor_text := paste0(round(cor, 2), "\n(", p.value, ")")] %>% 
#   dcast(type + term ~ season, value.var = "p.value") %>% 
#   .[, term := lab_sam[term]] 
table2 <- enso_cors %>% 
  .[index == "oni"] %>% 
  .[, p.value := p.adjust(p.value, "fdr")] %>% 
  # .[, p.value := scales::pvalue(p.value)] %>% 
  # .[, cor_text := paste0(round(cor, 2), "\n(", p.value, ")")] %>% 
  .[, term := lab_sam[term]] %>% 
  dcast(season ~ term, value.var = "p.value") %>% 
  setcolorder(c("season",lab_sam))

table %>% 
  kbl(escape = FALSE,
      caption = "Correlation between SAM indices and the Oceanic Niño Index. p-values corrected for False Detection Rate in parenthesis. In bold, correlations with p-value smaller than 0.05.",
      col.names = c("", lab_sam)) %>% 
  column_spec(2, bold = table2[, 2] < 0.05) %>%
  column_spec(3, bold = table2[, 3] < 0.05) %>%
  column_spec(4, bold = table2[, 4] < 0.05) %>%
  kable_paper(full_width = F) %>% 
  add_header_above(c(" " = 1, "Correlation" = 1 , "Partial correlation" = 2)) 
```

>>>>

```{r enso-cor-table}
table <- enso_cors %>% 
  .[index == "oni"] %>% 
  .[, p.value := p.adjust(p.value, "fdr")] %>% 
  .[, p.value := paste0("(", scales::pvalue(p.value), ")")] %>% 
  .[, cor_text := scales::number(cor, 0.01)] %>% 
  .[, term := lab_sam[term]] %>% 
  .[] %>% 
  melt(id.vars = c("term", "index", "season" ), measure.vars = c("cor_text", "p.value")) %>% 
  dcast(season + variable ~ term, value.var = "value") %>% 
  .[, variable := NULL] %>% 
  setcolorder(c("season", lab_sam))

table2 <- enso_cors %>% 
  .[index == "oni"] %>% 
  .[, p.value := p.adjust(p.value, "fdr")] %>%

  .[, term := lab_sam[term]] %>% 
  dcast(season ~ term, value.var = "p.value") %>% 
  setcolorder(c("season",lab_sam))

table %>% 
  kbl(align = "c", 
      caption = "Correlation between SAM indices and the Oceanic Niño Index. p-values corrected for False Detection Rate in parenthesis. In bold, correlations with p-value smaller than 0.05.", 
      col.names = c("", lab_sam), booktabs = TRUE) %>%
  kable_classic(full_width = F) %>%
  column_spec(2, bold = rep(table2[, 2] < 0.05, each = 2)) %>%
  column_spec(3, bold = rep(table2[, 3] < 0.05, each = 2)) %>%
  column_spec(4, bold = rep(table2[, 4] < 0.05, each = 2)) %>%
  collapse_rows(columns = 1:2, valign = "top") %>% 
  add_header_above(c(" " = 1, "Correlation" = 1, 
                     "Partial correlation" = 2)) 
```
